Visualizations for the manuscript

### 2022-05-10 metanalysis_visualization/manuscript_Figures.Rmd
forest plot update label and change the last line

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
dev.off()
```

>>>>

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                xlab = "Mean of the coefficients",
                mlab="Overall effect")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

forest.meta( x = model_meta_siteid)

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       xlab = "Mean of the coefficients",
       mlab="Overall effect")
dev.off()
```
